Type-Safe Modular Parsing

### 2016-10-18 paper/sections/CaseStudy.tex
Some text

\subsection{Overview}\label{subsec:overview}

@@

When composing the calculus from components, the \lstinline{Alg} and \lstinline{Print} can be easily combined by Scala’s \lstinline{extends...with} keywords as demonstrated in the code. For \lstinline{Parser}, the subtyping constraint for the explicit self-reference should satisfy all the requirement of the parsers it extends from. \huang{Talk about | here?}

Finally, we have demo code for every calculus. The parsing result is a string because we provide the pretty printing algebra to the parser, and it can be changed as long as the concrete algebra is available. Implementing object algebra operation is another topic which is not much relevant with our library, so that in this case study we only have pretty printing as the operation.

@@

\subsection{Extensibility}\label{subsec:extensibility}

As mentioned before, we decompose all the calculi into reusable components for modularity. In this case study, we have \textcolor{red}{18} components in total. The graph below shows the dependency of all the components, representing by circles, and calculi, representing by boxes.

\subsection{Comparison}\label{subsec:comparison}

>>>>

\subsection{Overview}\label{subsec:cs-overview}

@@

When composing the calculus from components, the \lstinline{Alg} and \lstinline{Print} can be easily combined by Scala’s \lstinline{extends...with} keywords as shown in the code. For \lstinline{Parser}, the subtyping constraint for the explicit self-reference should satisfy all the requirement of the parsers it extends from. \huang{Talk about | here?}

Finally, we have demo code for every calculus. The parsing result is a string because we provide the pretty printing algebra to the parser, and it can be changed as long as the concrete algebra is available. In this case study we only have pretty printing as the operation, since it is enough for demonstration.

@@

\subsection{Extensibility}\label{subsec:cs-extensibility}

As mentioned before, we decompose all the calculi into reusable components for modularity. In this case study, we have \textcolor{red}{21} components in total. The graph below shows the dependency of all the components, representing by circles, and calculi, representing by boxes. An arrow starting from shape A to shape B denotes that B includes and thus reuses A.

\textcolor{red}{graph here}

As shown in the graph, some components such as \lstinline{VarApp} are created from scratch, while others such as \lstinline{Typed} are extended from existing components. The \lstinline{Typed} component extends from \lstinline{VarApp} and has two more syntactical structures which are typed lambda abstraction and function type (arrow type). It is the core of many calculi in this case study, and we use it here as an example for demonstrating the extensibility of components.

\begin{lstlisting}
object Typed {
  trait Alg[E, T] extends VarApp.Alg[E] {
    def TmAbs(x: String, t: T, e: E): E
    def TyArr(t1: T, t2: T): T
  }
  trait Print extends Alg[String, String] with VarApp.Print {
    def TmAbs(x: String, t: String, e: String) = "\\(" + x + ":" + t + ")." + e
    def TyArr(t1: String, t2: String) = t1 + "->" + t2
  }
  trait Parser[E, T, F <: {val pE : PackratParser[E]; val pT : PackratParser[T]}] extends VarApp.Parser[E, F] {
    ...
    private val pAbsE: Alg[E, T] => (=> F) => PackratParser[E] = {...}
    val pTypedE: Alg[E, T] => (=> F) => PackratParser[E] = pVarAppE | pAbsE
    val pTypedT: Alg[E, T] => (=> F) => PackratParser[T] = alg => l => {
      val t = l.pT
      t ~ ("->" ~> t) ^^ { case t1 ~ t2 => alg.TyArr(t1, t2) } ||| "(" ~> t <~ ")"
    }
  }
}
\end{lstlisting}

Except building a component by extending an existing one, here we have another extension which is adding a new sort of syntax. It has been discussed in section \ref{subsec:openrecursion}. In this example, originally \lstinline{VarApp} has only one sort of syntax which is expressions, and then \lstinline{Typed} introduces types to the syntax. We add an extra type parameter \lstinline{T} for it, so that it is able to be distinguished. The \lstinline{Parser} also requires the self-reference to have a field \lstinline{pT} for parsing types, which is represented by the subtyping constraint. With this support, the \lstinline{pTypedT} function parses arrow types using \lstinline{pT}.

\subsection{Comparison}\label{subsec:cs-comparison}
